Are environmental and geographic effective surrogates for genetic variation in conservation planning?

### 2016-01-19 article/article.Rmd
scaffold for intro section of ms

@@

## Statistical analysis
We tested for differences in the effectiveness of prioritisations at securing genomic variation using general linear models (GLMs). These models were fit to the proportion of genomic variation explained using a logit link. They contained a predictor variable indicating if the prioritisation was generated using amount, surrogate, or genetic targets, a second predictor variable indicating if the genomic variation was adaptive or neutral, and the interaction between these variables. These models were subject to stepwise term deletion routes using likelihood ratio tests (LRT) to identify the minimal adequate model (terms were retained when $P < 0.05$).

>>>>

<!--
paragraph 1
topic sentence: biodiversity is in crisis (@rXX, @rXX).
	+ in recent years many species have gone extinct (@rXX).
	+ currently there are thousands of species listed as endangered or near threatened in the International Union for Conservation of Nature (IUCN) red list (www.iucnredlist.org).
	+ futhermore, climate change is expected cause even greater loss to global biodiversity (@rXXX).
linking sentence: in response to this crisis, the overarching aim of conservation is to ensure the persistance of biodiversity patterns and processes.
-->

Biodiversity is under threat. In recent years many species have gone extinct [@r272; @r270]. currently there are thousands of species listed as endangered or near threatened in the International Union for Conservation of Nature (IUCN) red list (www.iucnredlist.org). Futhermore, climate change is expected cause even greater loss to global biodiversity [@r236]. In response to this crisis, the overarching aim of conservation is to maximise the long-term persistance of conservation [@r255].

<!--
paragraph 2
topic sentence: the act of setting aside areas for the preservation of biodiversity is one the hallmarks of conservation.
	+ protected areas buffer species from anthropogenic impacts and provide areas for biodiversity processes to persist (eg. nutrient cycling and water purification).
	+ additionally, protected areas set the stage for direct management actions (eg. habitat rehabitilation, translocation, and invasive species management).
	+ since the resources avaliable for conservation are limited, the plans for protected areas (prioritizations) are often generated using biodiversity data (eg. species distribution data; @rXXX) , expressing the conservation planning problem as an optimisation problem, and solving it.
linking sentence:
-->

The act of setting aside areas for the preservation of biodiversity is one the hallmarks of modern conservation [@r440]. Protected areas buffer species from anthropogenic impacts and provide areas for biodiversity processes to persist (eg. nutrient cycling and water purification). Additionally, protected areas set the stage for direct management actions (eg. habitat rehabitilation, translocation, and invasive species management). Since the resources avaliable for conservation are limited, the plans for protected areas (prioritizations) are often generated by using biodiversity data and decision support tools [eg. \texttt{MARXAN}, @r22; \texttt{Zonation}, @r429] to identify cost-effective prioritizations.

<!--
paragraph 3
topic sentence: intra-specific genetic variation is important for species persistance.
	+ Genetic variation is classified as either adaptive or neutral. 
	+ Adaptive genetic variation refers to loci currently under selectiom.
	+ Neutral genetic variation to loci that are not under selection, and reflects the evolutionary history of populations.
	+ By preserving existing patterns of adaptive genetic variation, protected areas can ensure that populations with particularly beneficial adaptations are not lost.
	+ In constrast, by preserving existing patterns of neutral genetic variation, protected areas can secure populations belonging to genetic lineages and avoid inbreeding depresssion.
	+ Protected areas must preserve a representative sample of both of these types of genetic variation to fulfil the overarching aims of conservation.
linking sentence: However, genetic data is costly to obtain and requires expert knowledge to process for use in conservation planning. As a consequence, genetic data is not used to inform large-scale prioritisations, and so these prioritisations may fail to preserve the intra-specific genetic variation for the species they aim to preserve.
-->

<!--
paragraph 5
topic sentence: Cost-effective surrogate data could be used to identify prioritizations that preserve intra-specific genetic variation.
+ Adaptive genetic variation is driven by selection pressures.
+ Conservation planners have explored the use of data on the distribution of likely selection pressures to generate prioritizations to secure adaptive genetic variation [eg. @rXXX; @rXXX; @rXXXX].
+ On the other hand, neutral genetic variation arises due to the break down of gene flow between populations.
+ Conservation planners have explored the use of variables that predict a reduction in gene flow between populations.
+ The isolation by distance theory [IBD; @rXX] predicts that populations are further apart will have lower gene flow.
+ The use of geographical surrogate data has been found to improve prioritisations in an island network [@rXX].
+ However this remains untested in system with in a terrestrial study system where connectivity is affected additional factors (eg. elevation).
linking sentence:
-->

<!--
paragraph 6
topic sentence: The aim of this study is to investigate the effectiveness of environmental and geographic surrogates for conservation planning.
	+ First, we aim to test the effectiveness of these surrogates under the simplest of conditions in a set of single-species prioritisations.
	+ Second, we aim to test the effectiveness of these surrogates in a more realistic multi-species context.
	+ Third, we aim to understand the relationship between the proportion of surrogate variation secured in a multi-species prioritisation and the prorpotion of genetic variation secured in a prioritization.
linking sentence:
-->

@@

## Statistical analysis
We tested for differences in the effectiveness of prioritisations at securing genomic variation using generalized linear mixed-effects models (GLMMs). These models were fit to the proportion of genomic variation explained using a logit link. They contained a predictor variable indicating if the prioritisation was generated using amount, surrogate, or genetic targets, a second predictor variable indicating if the genomic variation was adaptive or neutral, and the interaction between these variables. All models contained an intercept-only random effect to ensure that comparisons were made between species. These models were subject to stepwise term deletion routes using likelihood ratio tests (LRT) to assess term significance and identify the minimal adequate model (terms were retained when $P < 0.05$).
